### 2012-12-21 inst/examples/myers-exploration.Rmd
Ah here we go! with a decent allee effect model, the results are much clearer!

```{r }
seed <- round(runif(32) * 1e6)
seed[1] <- 1
seed
yields <- lapply(seed, 
function(seed_i){
  Xo <- allee + x_grid[5] # observations start from
  x0 <- 2 # simulation under policy starts from
  obs <- sim_obs(Xo, z_g, f, p, Tobs=40, seed = seed_i)
  est <- par_est(obs)
  gp <- bgp(X=obs$x, XX=x_grid, Z=obs$y, verb=0,
          meanfn="constant", bprior="b0", BTE=c(2000,16000,2),
          m0r1=FALSE, corr="exp", trace=FALSE, 
          beta = beta, s2.p = s2.p, d.p = d.p, nug.p = nug.p, tau2.p = tau2.p,
          s2.lam = "fixed", d.lam = "fixed", nug.lam = "fixed", tau2.lam = "fixed")      
  gp_plot(gp, f, p, est$f_alt, est$p_alt, x_grid, obs, seed_i)
  OPT <- optimal_policy(gp, f, est$f_alt, p, est$p_alt, x_grid, h_grid, sigma_g, est$sigma_g_alt, delta, xT, profit, reward, OptTime)
  dt <- simulate_opt(OPT, f, p, x_grid, h_grid, x0, z_g, profit)
  sim_plots(dt, seed=seed_i)
  profits_stats(dt)
})
```

>>>>

```{r }
seed <- round(runif(32) * 1e6)
seed[1] <- 1
seed
yields <- lapply(seed, 
function(seed_i){
  Xo <- allee + x_grid[10] # observations start from
  x0 <- Xo # simulation under policy starts from
  obs <- sim_obs(Xo, z_g, f, p, Tobs=40, seed = seed_i)
  est <- par_est(obs)
  gp <- bgp(X=obs$x, XX=x_grid, Z=obs$y, verb=0,
          meanfn="constant", bprior="b0", BTE=c(2000,16000,2),
          m0r1=FALSE, corr="exp", trace=FALSE, 
          beta = beta, s2.p = s2.p, d.p = d.p, nug.p = nug.p, tau2.p = tau2.p,
          s2.lam = "fixed", d.lam = "fixed", nug.lam = "fixed", tau2.lam = "fixed")      
  gp_plot(gp, f, p, est$f_alt, est$p_alt, x_grid, obs, seed_i)
  OPT <- optimal_policy(gp, f, est$f_alt, p, est$p_alt, x_grid, h_grid, sigma_g, est$sigma_g_alt, delta, xT, profit, reward, OptTime)
  dt <- simulate_opt(OPT, f, p, x_grid, h_grid, x0, z_g, profit)
  sim_plots(dt, seed=seed_i)
  profits_stats(dt)
})
```
